---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

# Plot Analysis

```{r}
library(readxl)
library(forecast)
data <- read_excel(file.choose())
y <- ts(data$electricity_consumption, start = 1971, end = 2023)
plot(y, xlab = "Year", ylab = "kWh/Capita")
```

## We can conclude from the time series plot that the data is following a trend.

# Data Splitting (95:5)

```{r}
ntrain = round(nrow(data)*0.95)
ntrain

ntest = nrow(data)-ntrain
ntest

train <- window(y, start = 1971, end = 1971+ntrain-1)
test <- window(y, start = 1971+ntrain, end = 2023)

t <- seq(1:ntrain)
```

## Because we're using yearly data, we'll be doing a 95:5 Train-Test Split, from 53 entry we split it to 50:3 respectively for train and test data. Train data starts form 1971 to 2020 and test data starts from 2021 to 2023.

# Double Exponential Smoothing Model Training
```{r}
des <- holt(train, h = ntest)
summary(des)
```

# Double Exponential Smoothing Model Testing

```{r}
# Predict
despred <- des$mean

# RMSE of Test Model
sqrt(mean((despred-test)^2))

# MAE of Test Model
mean(abs(despred-test))

# MAPE of Test Model
mean(abs((despred-test)/test)) * 100
```

# Regression Model Training

## Model 1

```{r}
regModel <- lm(train ~ t)
summary(regModel)
```

```{r}
library(nortest)
library(lmtest)

# Normality Test
resid <- resid(regModel)
lillie.test(resid)

# Independence Test
dwtest(regModel)

# Homoscedasticity Test
bptest(regModel)
```

## We can see that we failed both independence assumption and normality assumption at alpha = 0.05. We will be testing our data on other models.

## Model 2

```{r}
regModel2 <- lm(log(train) ~ t)
summary(regModel2)

# Normality Test
resid2 <- resid(regModel2)
lillie.test(resid2)

# Independence Test
dwtest(regModel2)

# Homoscedasticity Test
bptest(regModel2)
```

## Model 3

```{r}
regModel3 <- lm(train ~ t + I(t^2))
summary(regModel3)

# Normality Test
resid3 <- resid(regModel3)
lillie.test(resid3)

# Independence Test
dwtest(regModel3)

# Homoscedasticity Test
bptest(regModel3)
```

## Model 4

```{r}
yt <- train[2:ntrain]
yt1 <- train[1:(ntrain-1)]
tn <- t[2:ntrain]

regModel4 <- lm(yt ~ tn + yt1)
summary(regModel4)

# Normality Test
resid4 <- resid(regModel4)
lillie.test(resid4)

# Independence Test
dwtest(regModel4)

# Homoscedasticity Test
bptest(regModel4)
```

## Model 5

```{r}
yt <- train[2:ntrain]
yt1 <- train[1:(ntrain-1)]
tn <- t[2:ntrain]

regModel5 <- lm(yt ~ tn + yt1 - 1)
summary(regModel5)

# Normality Test
resid5 <- resid(regModel5)
lillie.test(resid5)

# Independence Test
dwtest(regModel5)

# Homoscedasticity Test
bptest(regModel5)
```

# ARIMA Model Training

```{r}
# Variance Stationarity Test
library(car)
summary(powerTransform(train))
```

## Data is not stationary against variance, we'll be taking lambda = (0) and log our data.

```{r}
trainTransformed <- log(train)
summary(powerTransform(trainTransformed))
```

## Transformed data is stationary against variance, moving to next step.

```{r}
# Mean Stationarity Test
library(tseries)
adf.test(trainTransformed)
# Data is not stationary against Mean

# We'll try differencing
d1 <- diff(trainTransformed)
adf.test(d1)
# Stationary, we'll proceed using differencing 1.
```

## ACF & PACF Test

```{r}
# ACF
acf(d1, lag.max=10)

# Order of q Combination (0, 1)
```

```{r}
# PACF
pacf(d1, lag.max=10)

# Order of p Combination (0, 1, 2, 3)
```

```{r}

arimaModel1 <- arima(trainTransformed, order = c(0, 0, 1))
coeftest(arimaModel1)

arimaModel2 <- arima(trainTransformed, order = c(1, 0, 0))
coeftest(arimaModel2)

arimaModel3 <- arima(trainTransformed, order = c(2, 0, 0))
coeftest(arimaModel3)

arimaModel4 <- arima(trainTransformed, order = c(0, 1, 1))
coeftest(arimaModel4)

arimaModel5 <- arima(trainTransformed, order = c(1, 1, 0))
coeftest(arimaModel5)

arimaModel6 <- arima(trainTransformed, order = c(1, 1, 1))
coeftest(arimaModel6)

arimaModel7 <- arima(trainTransformed, order = c(3, 1, 0))
coeftest(arimaModel7)
```

## We got 3 significant model but without order AR because as we can see in the graph of AR, it dies down.

```{r}
# Assumption Testing
res1 <- residuals(arimaModel1)
res2 <- residuals(arimaModel2)
res3 <- residuals(arimaModel3)
res4 <- residuals(arimaModel4)
res5 <- residuals(arimaModel5)
res6 <- residuals(arimaModel6)
res7 <- residuals(arimaModel7)

# Normality Assumption Using Kolmogorov-Smirnov Test
lillie.test(res1)
lillie.test(res2)
lillie.test(res3)
lillie.test(res4)
lillie.test(res5)
lillie.test(res6)
lillie.test(res7)

# White Noise Assumption Using Ljung-Box Test
Box.test(res1)
Box.test(res2)
Box.test(res3)
Box.test(res4)
Box.test(res5)
Box.test(res6)
Box.test(res7)
```

## We will proceed with model 2 and 7 since they both passed the assumption test.

# Arima Model 2 

```{r}
# Training Accuracy
fittedRetransformed <- exp(fitted.values(arimaModel2))

# RMSE of Train Model
sqrt(mean((fittedRetransformed-train)^2))

# MAE of Train Model
mean(abs(fittedRetransformed-train))

# MAPE of Train Model
mean(abs((fittedRetransformed-train)/train)) * 100
```

```{r}
arimaForecast <- forecast(arimaModel2, ntest)
arimapred <- exp(arimaForecast$mean)

# RMSE of Test Model
sqrt(mean((arimapred-test)^2))

# MAE of Test Model
mean(abs(arimapred-test))

# MAPE of Test Model
mean(abs((arimapred-test)/test)) * 100
```

# Arima Model 7

```{r}
# Training Accuracy
fittedRetransformed <- exp(fitted.values(arimaModel7))

# RMSE of Train Model
sqrt(mean((fittedRetransformed-train)^2))

# MAE of Train Model
mean(abs(fittedRetransformed-train))

# MAPE of Train Model
mean(abs((fittedRetransformed-train)/train)) * 100
```

```{r}
arimaForecast <- forecast(arimaModel7, ntest)
arimapred <- exp(arimaForecast$mean)

# RMSE of Test Model
sqrt(mean((arimapred-test)^2))

# MAE of Test Model
mean(abs(arimapred-test))

# MAPE of Test Model
mean(abs((arimapred-test)/test)) * 100
```
